---
title: "VDJ_BC_analysis"
author: "Chau"
date: "2024-06-26"
output: html_document
---

#Load libraries 
```{r}
library(data.table)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(Seurat)
library(plotly)
```

```{r}
#load(file = "/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/RObject/BC/merge_2023exp_reg_cc.Robj")
TCR_Data_230303_pass <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230303/filtered_contig_igblast_db-pass.tsv', sep = '\t', header = TRUE)
TCR_Data_230303_fail <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230303/filtered_contig_igblast_db-fail.tsv', sep = '\t', header = TRUE)
TCR_Data_230320_pass <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230320/filtered_contig_igblast_db-pass.tsv', sep = '\t', header = TRUE)
TCR_Data_230320_fail <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230320/filtered_contig_igblast_db-fail.tsv', sep = '\t', header = TRUE)
TCR_Data_230327_pass <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230327/filtered_contig_igblast_db-pass.tsv', sep = '\t', header = TRUE)
TCR_Data_230327_fail <- read.table(file = '/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/TCR/BALBC/230327/filtered_contig_igblast_db-fail.tsv', sep = '\t', header = TRUE)
```

#Dataframe formating
```{r}
#Create a function to trim the cell_id and append sample information before barcodes
barcoder <- function(df, trim="\\-1", sample) {
  df$cell_id <- gsub(trim, "", df$cell_id)
  df$cell_id <- paste0(sample,"_", df$cell_id)
  df[df == ''] <- NA
  return(df)
}
TCR_Data_230303_pass <- barcoder(TCR_Data_230303_pass ,sample = "230303")
TCR_Data_230303_fail<- barcoder(TCR_Data_230303_fail ,sample = "230303")
TCR_Data_230320_pass <- barcoder(TCR_Data_230320_pass ,sample = "230320")
TCR_Data_230320_fail<- barcoder(TCR_Data_230320_fail ,sample = "230320")
TCR_Data_230327_pass <- barcoder(TCR_Data_230327_pass ,sample = "230327")
TCR_Data_230327_fail<- barcoder(TCR_Data_230327_fail ,sample = "230327")
```
When re running on mouse genome in the pass TCR there is no TRA. They are all in the don't pass filter
In makeDB.py doc this is due to this possibilities :
- no productivity information
- no gene V assignment
- no J assignment
- no junction region.
```{r}
#Explore TCR data 
##TCR pass
length(TCR_Data_230303_pass$locus=='TCRB') # In the pass TCR there is no TRA, all are TCRB
##TCR fail
length(TCR_Data_230303_fail$productive==TRUE) # All are productive
sum(is.na(TCR_Data_230303_fail$v_call)) # They have all V assignment 
factor(unique(TCR_Data_230303_fail$v_call)) # But some have more than one V assignment
sum(is.na(TCR_Data_230303_fail$j_call))# They have all J assignment 
factor(unique(TCR_Data_230303_fail$j_call)) # Some have two j genes : TRAJ31*01 and TRAJ31*02; TRAJ12*01 and TRAJ12*02
sum(is.na(TCR_Data_230303_fail$junction)) # They have all junction region
```

# Combine all TRA and TRB based on barcodes
```{r}
TCRAB_230303 <- bind_rows(TCR_Data_230303_pass, TCR_Data_230303_fail)
TCRAB_230320 <- bind_rows(TCR_Data_230320_pass, TCR_Data_230320_fail)
TCRAB_230327 <- bind_rows(TCR_Data_230327_pass, TCR_Data_230327_fail)
length(unique(TCRAB_230303$cell_id)) #number of cells for which we have TCR information
length(unique(TCRAB_230320$cell_id))
length(unique(TCRAB_230327$cell_id))
```

# Extract some relevant informations from the full dataframes
```{r}
TCRAB_230303_extract <- subset(TCRAB_230303, select = c("cell_id","locus", "v_call", "d_call", "j_call", "c_call"))
TCRAB_230320_extract <- subset(TCRAB_230320, select = c("cell_id","locus", "v_call", "d_call", "j_call", "c_call"))
TCRAB_230327_extract <- subset(TCRAB_230327, select = c("cell_id","locus", "v_call", "d_call", "j_call", "c_call"))
TCR_all <- bind_rows(TCRAB_230303_extract,TCRAB_230320_extract, TCRAB_230327_extract)
```

```{r}
#Function to generate V(D)J genotype of each cell
makeCTgenes <- function(df, chainA = "TRA", chainB = "TRB") {
  # Create TCRA and TCRB columns
  df <- df %>%
    mutate(TCRA = if_else(locus == chainA, str_c(str_replace_na(v_call), str_replace_na(j_call), str_replace_na(c_call), sep = "."), NA_character_)) %>%
    mutate(TCRB = if_else(locus == chainB, str_c(str_replace_na(v_call), str_replace_na(d_call), str_replace_na(j_call), str_replace_na(c_call), sep = "."), NA_character_))
  df <- df %>%
    group_by(cell_id) %>%
    summarize(
      TCRA = str_c(unique(na.omit(TCRA)), collapse = "+"), # Concatenate unique non-NA TCRA values
      TCRB = str_c(unique(na.omit(TCRB)), collapse = "+")) %>% # Concatenate unique non-NA TCRB values
    mutate(across(c(TCRA, TCRB), ~na_if(.x, "")))# Replace empty strings with NA to ensure NAs are represented correctly
  df$CTgene <- str_c(str_replace_na(df$TCRA), str_replace_na(df$TCRB), sep = "_")
    return(df)
}
TCRgenotype_all <- makeCTgenes(TCR_all)
write.csv(TCRgenotype_all, file = "/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/outputs/TCR_genotype_BC.csv", row.names=FALSE)
```

```{r}
#check outputs with the results of Cellranger & scRepertoire
bc.combined.vdj@meta.data["230320_CGCTATCCATCACGTA",]
TCRgenotype_all["230320_CGCTATCCATCACGTA",]
```

```{r}
TCRgenotype_all <- read.csv("/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/outputs/BC/TCR_genotype_BC.csv")
```

# Defining OTII status of cells
```{r}
OTII <- TCRgenotype_all[with(TCRgenotype_all, grepl('^TRAV14.*TRAJ31.*_.*TRBV12-2.*TRBJ2-4.*', CTgene) & !grepl('.*\\+.*', CTgene)),]
OTIItrav <- TCRgenotype_all[with(TCRgenotype_all, grepl('^TRAV14.*TRAJ31.*_NA', CTgene)),]
OTIItrbv <- TCRgenotype_all[with(TCRgenotype_all, grepl('^NA_TRBV12-2.*TRBJ2-4.*', CTgene)),]
OTIImultiTRAV <- TCRgenotype_all[with(TCRgenotype_all, grepl('.*TRAV14.*TRAJ31.*_.*TRBV12-2.*TRBJ2-4.*', CTgene) & grepl('.*\\+.*_.*', CTgene)),]
OTIImultiTRBV <- TCRgenotype_all[with(TCRgenotype_all, grepl('.*TRAV14.*TRAJ31.*_.*TRBV12-2.*TRBJ2-4.*', CTgene) & grepl('.*_.*\\+.*', CTgene)),]
OTII_all <- bind_rows(OTII, OTIItrav, OTIItrbv, OTIImultiTRAV, OTIImultiTRBV)
nonOTII <- setdiff(TCRgenotype_all$cell_id, OTII_all$cell_id)
cells_used <-rownames(bc.combined.cc@meta.data)

#Adding annotation of OTII status to metadata
bc.combined.cc@meta.data$OTIIstatus <- "unknown"
bc.combined.cc@meta.data[intersect(OTII$cell_id,cells_used),]$OTIIstatus <- "OTII"
bc.combined.cc@meta.data[c(intersect(OTIItrav$cell_id,cells_used),intersect(OTIItrbv$cell_id,cells_used)),]$OTIIstatus <- "OTII - incomplete"
bc.combined.cc@meta.data[c(intersect(OTIImultiTRAV$cell_id,cells_used),intersect(OTIImultiTRBV$cell_id,cells_used)),]$OTIIstatus <- "OTII - multichains"
bc.combined.cc@meta.data[intersect(nonOTII,cells_used),]$OTIIstatus <- "non OTII"

```


# Details infos are stored in 'OTII_geno'
```{r}
bc.combined.cc@meta.data$OTII_geno <- "unknown"
bc.combined.cc@meta.data[intersect(OTII$cell_id,cells_used),]$OTII_geno <- "OTII"
bc.combined.cc@meta.data[intersect(OTIItrav$cell_id,cells_used),]$OTII_geno <- "OTII - Trbv missing"
bc.combined.cc@meta.data[intersect(OTIItrbv$cell_id,cells_used),]$OTII_geno <- "OTII - Trav missing"
bc.combined.cc@meta.data[intersect(OTIImultiTRAV$cell_id,cells_used),]$OTII_geno <- "OTII - multi-Trav"
bc.combined.cc@meta.data[intersect(OTIImultiTRBV$cell_id,cells_used),]$OTII_geno <- "OTII - multi-Trbv"
bc.combined.cc@meta.data[intersect(nonOTII,cells_used),]$OTII_geno <- "non OTII"
```

# Save object
```{r}
save(bc.combined.cc, file = "/mnt/NASBIOINFO_CP/LALT/BIOINFO/PTEN/03_Analysis/Analysis2024/RObject/merge_2023exp_reg_cc.Robj")
```

```{r}
# Classer PreTum early , PreTum late = Pre-Tum
bc.combined.cc@meta.data$annotation[which(bc.combined.cc@meta.data$annotation =="Thymus-PreTum early")] <- "Thymus-PreTum late"
bc.combined.cc@meta.data$annotation[which(bc.combined.cc@meta.data$annotation %in% "Spleen-PreTum early")] <- "Spleen-PreTum late"
```

# Distribution of OTII status in Thymus BC OTII
```{r}
Idents(bc.combined.cc) <- "OTIIstatus"
OTIIbc <- subset(bc.combined.cc, idents = c("OTII","OTII - multichains","non OTII"))# Remove 'unknown' and 'OTII- incomplete" because not informative
Idents(OTIIbc) <- "annotation"
Thymusbc <- subset(OTIIbc, idents = c("Thymus-WT","Thymus-PreTum late","Thymus-Tum"))
data1 <- as.data.frame(prop.table(table(Thymusbc@meta.data$OTIIstatus,Thymusbc@meta.data$annotation),2)*100)
#data1 <-na.omit(data1)
data1 <- data1[!(data1$Freq=="NaN"), ]
#order leukestage level
data1$Var2 <- factor(data1$Var2, levels = c("Thymus-WT","Thymus-PreTum late","Thymus-Tum"))
cellnumber <- data.frame(colSums(table(Thymusbc@meta.data$MULTI_ID,Thymusbc@meta.data$annotation)))
cellnumber <- subset(cellnumber,rownames(cellnumber) %in% c("Thymus-WT","Thymus-PreTum late","Thymus-Tum"))
cellnumber$annotation <- rownames(cellnumber)
row_order <-c("Thymus-WT","Thymus-PreTum late","Thymus-Tum")
cellnumber <- cellnumber[row_order,]
annotation <- data1$Var2
OTII_status <- data1$Var1
OTII_status <- factor(OTII_status, levels = rev(c("OTII","OTII - multichains", "non OTII"))) 
Percentage <- data1$Freq
text <- cellnumber$colSums.table.Thymusbc.meta.data.MULTI_ID..Thymusbc.meta.data.annotation..
ggplot(data1, aes(fill=OTII_status, y=Percentage, x=annotation)) + 
    geom_bar(position="stack", stat="identity", width=0.7)+
   xlab("Stade of leukemia")+ylab("Percentage")+ theme(legend.position="bottom")+scale_fill_manual(values = OTIIpalette) +theme_light()+geom_hline(yintercept=c(25,50,75), linetype="dashed", color = "black")+ annotate("text", x = 1:3, y=103, label = c(text)) + labs(title = "Distribution of OTII status in Thymus BC OTII ")
DimPlot(Thymusbc, group.by = "OTIIstatus", split.by = "annotation", reduction = "umap" ,cols = OTIIpalette, pt.size = 0.5, ncol= 3) + labs(title = "OTII status")
```

# Radarplot : distribution of cell types in each OTIIstatus 
```{r}
Idents(bc.combined.cc) <- "OTIIstatus"
OTIIbc <- subset(bc.combined.cc, idents = c("OTII","OTII - multichains","non OTII"))
Idents(OTIIbc) <- "annotation"
Thymusbc <- subset(OTIIbc, idents = c("Thymus-WT","Thymus-PreTum late","Thymus-Tum"))
ThymusWTbc <- subset(Thymusbc, idents = c("Thymus-WT"))
df_radarchartWT<-as.data.frame(prop.table(table(ThymusWTbc@meta.data$sig.annotation,ThymusWTbc@meta.data$OTIIstatus),2)*100)
colnames(df_radarchartWT) <- c( "Annotation","OTIIstatus","Proportion")

ThymusPreTumbc <- subset(Thymusbc, idents = c("Thymus-PreTum late"))
df_radarchartPreTum<-as.data.frame(prop.table(table(ThymusPreTumbc@meta.data$sig.annotation,ThymusPreTumbc@meta.data$OTIIstatus),2)*100)
colnames(df_radarchartPreTum) <- c( "Annotation","OTIIstatus","Proportion")

ThymusTumbc <- subset(Thymusbc, idents = c("Thymus-Tum"))
df_radarchartTum<-as.data.frame(prop.table(table(ThymusTumbc@meta.data$sig.annotation,ThymusTumbc@meta.data$OTIIstatus),2)*100)
colnames(df_radarchartTum) <- c( "Annotation","OTIIstatus","Proportion")

df_list <- list(df_radarchartWT, df_radarchartPreTum, df_radarchartTum)
df_combined <- NULL
  for (i in seq_along(df_list)) {
    df_i <- subset(df_list[[i]], OTIIstatus == "OTII")
      df_ti <- data.frame(t(df_i[,"Proportion"]))
      colnames(df_ti) <- df_i$Annotation
      # Ajouter chaque data frame transformé au data frame combiné
      df_combined <- rbind(df_combined, setNames(df_ti, colnames(df_ti)))
      col_names <- c(col_names, paste(colnames(df_ti), labels[i], sep=" - "))
  }
df_combined <- rbind(rep(60, 21), rep(0, 21),df_combined)[, 1:21]
rownames(df_combined) <- c("Max","Min","Thymus-WT","Thymus-PreTum","Thymus-Tum")
op <- par(mar = c(1, 1, 1, 1))  # Ajuster les marges
radarchart(df_combined, cglcol="black", cglty=2, cglwd=1, vlcex=1,
               pcol="#7AD151FF",pty = 20, plty=1:3, 
               caxislabels=paste(seq(from=0, to=60, by=15), "%"),
               axislabcol="black", axistype=4,
               title=paste("OTII"),
               plwd=4)

# Ajouter une légende
#legend("topright", legend=rownames(df_combined)[3:5], lty=linetypes, lwd=2, cex=0.8)
node_labels <- colnames(df_combined)
node_positions <- seq(0, 2 * pi, length.out = length(node_labels) + 1)[-1]
node_r <- rep(60, length(node_labels))  # Distance pour chaque nœud
text_pos_x <- cos(node_positions) * (node_r + 5)  # Ajuster la position x
text_pos_y <- sin(node_positions) * (node_r + 5)  # Ajuster la position y
text_labels <- colnames(df_combined)

# Tracer les étiquettes
text(text_pos_x, text_pos_y, labels = text_labels, cex = 0.8)

par(op)
```

# Visualization 
```{r}
OTIIpalette <- c("#FDE725FF","#414487FF","#DE4968FF","#7AD151FF","#808080FF")
names(OTIIpalette) <- c("OTII","OTII - incomplete","OTII - multichains","non OTII","unknown")
DimPlot(bc.combined.cc, group.by = "OTIIstatus",split.by = "OTIIstatus", reduction = "wnn.umap", cols = OTIIpalette, pt.size = 0.5)
DimPlot(bc.combined.cc, group.by = "OTIIstatus", split.by = "annotation", reduction = "wnn.umap", cols = OTIIpalette, pt.size = 0.5)


FeaturePlot(bc.combined.cc, features = c("adt_TCR-VB5","Trbv12-2","adt_TCR-VA2","Trav14n-1"), reduction = "wnn.umap") & scale_colour_gradientn(colours = rev(viridis::magma(10)))|DimPlot(bc.combined.cc, reduction = "wnn.umap", cells.highlight = Vb5$cell_id, cols = "#FCFDBFFF",cols.highlight = "#DD513AFF", pt.size = 0.5,sizes.highlight = 0.5)| DimPlot(bc.combined.cc, reduction = "wnn.umap", cells.highlight = Va2$cell_id, cols = "#FCFDBFFF",cols.highlight = "#DD513AFF", pt.size = 0.5,sizes.highlight = 0.5)
```

```{r}
FeaturePlot(bc.combined.cc, features = c("adt_TCR-VA2","adt_TCR-VB5"),order = T, reduction = "wnn.umap", pt.size = 0.2, ncol = 2 ) & scale_colour_gradientn(colours = rev(viridis::rocket(10)))
Idents (bc.combined.cc) <- "annotation"
DimPlot(bc.combined.cc, group.by = "MULTI_ID",split.by="miceID",order = rev(c("51","83","47","85","84","39","52","70","80","53","69")) , reduction = "wnn.umap", pt.size = 0.5, label = TRUE, repel = TRUE, label.size = 2.5, ncol = 4, cols = multi_id.palette)
```

```{r}
Idents(bc.combined.cc) <- "sig.annotation"
VlnPlot(bc.combined.cc, features = c("Trbv12-2"), ncol = 1,group.by = "sig.annotation",idents = c("DPsm","DPsmCD25+","DPsmCCR7+","DP69","SP8","SP4","SP4CD69+","DPsm Myc+","DP69 Myc+","Undefined Myc+") , pt.size = 0, y.max = 4, cols = c(palette1,palette2,palette3,palette4) )& theme(plot.title = element_text(hjust = 0.5,face = "bold")) & geom_boxplot(width=0.1, fill="white")

Idents(bc.combined.cc) <- "miceID"
bc.combined.cc$miceID <- factor(bc.combined.cc$miceID, levels=c("51","83","39","47","52","84","85","70","80","53","69"))
VlnPlot(bc.combined.cc, features = c("adt_TCR-VB5"), ncol = 1,group.by = "miceID", pt.size = 0, y.max = 3, cols = c(rep("#9AC4F8",2),rep("#fac341",6),rep("#BB0A21",3)))& theme(plot.title = element_text(hjust = 0.5,face = "bold")) & geom_boxplot(width=0.1, fill="white")
Idents(bc.combined.cc) <- "miceID"
VlnPlot(bc.combined.cc, features = c("adt_TCR-B"), ncol = 1,group.by = "miceID", pt.size = 0,y.max = 3, cols = c(rep("#9AC4F8",2),rep("#fac341",6),rep("#BB0A21",3)))& theme(plot.title = element_text(hjust = 0.5,face = "bold")) & geom_boxplot(width=0.1, fill="white")
```

```{r}
Idents(bc.combined.cc) <- "miceID"
VlnPlot(bc.combined.cc, features = c("Trbv17","Trbv16","Trbv31","Trbv2","Trbv20","Trbv15","Trbv13-1"),group.by = "miceID", pt.size = 0, ncol = 2)+ theme(legend.position = "none")

VlnPlot(bc.combined.cc, features = c("Trbv16","Trbv2","Trbv15","Trbv13-1"),group.by = "miceID", pt.size = 0,idents = c("39","47","52","84","85","70"), ncol = 1, cols= rep("#fac341",6))+ theme(legend.position = "none")
VlnPlot(bc.combined.cc, features = c("Trbv17","Trbv31","Trbv20"), group.by = "miceID", pt.size = 0, ncol = 1, idents = c("80","53","69"), cols = rep("#BB0A21",3) )+ theme(legend.position = "none")
```

